Abstractions for Type-Level Programming

### 2022-04-21 article.tex
Tell the truth about empty types

% TODO: tell the truth about empty types

@@

In practice, the Scala compiler copes with this limitation by emitting warnings for unchecked patterns.
For example, while |case xs: List[Int] =>| is a syntactically valid pattern, it compiles with a warning the |Int| type parameter is eliminated by erasure and cannot be checked at runtime.

@@

In the absence of result type annotation, Scala's type inference will first assign \lstinline!String | Int! for the match expression, and then immediately widen that union to the least upper bound of left- and right-hand-side, |Any|, which will then be used as |foo|'s (inferred) result type.
To obtain a precise result type for this method, users should annotate it explicitly:

>>>>

In practice, it would be quite restrictive to only reduce match types with provably inhabited scrutinees since it would disallow matching on abstract types.
Instead, our implementation incorporates non-emptyness in the
definition of the disjointness relation:

$disj(T1, T2) = T1 nonempty and \forall e \in T1. e \notin T2$

This updated definition allows us to maintain the property of \Cref{lem:disjointness-subtyping-exclusivity} in the presence of empty types (disjointness/subtyping exclusivity).

% TODO: tell the truth about empty types?

@@

In practice, the Scala compiler handles this limitation by emitting warnings for unchecked patterns.
For example, while |case xs: List[Int] =>| is a syntactically valid pattern, it compiles with a warning the |Int| type parameter is eliminated by erasure and cannot be checked at runtime.

@@

In the absence of result type annotation, Scala's type inference will first assign \lstinline!String|Int! for the match expression, and then immediately widen that union to the least upper bound of left- and right-hand-side, |Any|, which will then be used as |foo|'s (inferred) result type.
To obtain a precise result type for this method, users should annotate it explicitly:
